Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-09 paper/tex/sections/results.tex
eccentricity and chirp mass uncertainty

\subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}
\todo{will fill with info on eccentricity, chirp mass and angular resolution uncertainties}

>>>>

\subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}
Although it is useful to investigate the underlying parameters of the detectable population, it is also important to consider what LISA will actually \textit{measure} during a detection.

\subsubsection{Eccentricity uncertainty}\label{sec:ecc_unc}
One of the main advantage of space-based gravitational wave detectors such as LISA is that systems may still have significant eccentricity during the LISA mission. Whilst also being useful a useful individual quantity for learning more about sources, the uncertainty on the eccentricity also affects the uncertainty on the chirp mass and so it is important to quantify this uncertainty.

We follow a method used in previous works that uses the individually detectable harmonics of sources to determine the uncertainty of the eccentricity of a source \citep[e.g.][]{Lau+2020, Korol+2021}. Eccentric sources emit at several evenly spaced harmonic frequencies, each with a different fraction of the gravitational wave power and the distribution of the power over the harmonics changes with eccentricity. Therefore, by measuring the SNR of each individual harmonic and finding the ratio of the SNR of the two most detectable harmonics that are above the detection threshold, one can determine the eccentricity. The uncertainty on the eccentricity can therefore be written as a combination of the uncertainty on the SNR of the two most detectable harmonics. In the limit of large SNRs, the eccentricity uncertainty, $\Delta e$, can be written as 
\begin{equation}
    \Delta e = \frac{1}{\rho_1} + \frac{1}{\rho_2},
\end{equation}
where $\rho_1$ and $\rho_2$ are the SNRs of the two most detectable harmonics.

In some cases, sources may only have one individually detectable harmonics, or even none. In these cases one can only put a lower or upper bound on the eccentricity. For sources with only one detectable harmonic, the source is either a circular source or a source with a small enough eccentricity that most of the GW power is still concentrated in the $n = 2$. Therefore, we can use this information to place an upper bound on the eccentricity. Conversely, sources with no detectable harmonics must be eccentric such that the GW power has spread over so many harmonics that no single harmonic has a significantly stronger signal. Therefore, we can use this information to place a lower bound on the eccentricity.

This method provides a pessimistic estimate of the eccentricity of sources since we do not consider the benefits of any sort of matched-filter analysis or similar methods. We discuss how the pessimism of this method affects our results and some possible alternative in Section~\ref{sec:caveats}.

\subsubsection{Chirp mass uncertainty}
The chirp mass uncertainty can be calculated using the uncertainty on the orbital frequency, the time derivative of the orbital frequency and the eccentricity. This is because the time derivative of the orbital frequency can be written as
\begin{equation}
    \dot{f}_{\rm orb} = \frac{48}{5 \pi} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} (2 \pi f_{\rm orb})^{11/3} F(e),
\end{equation}
where $f_{\rm orb}$ is the orbital frequency, $\mathcal{M}_{c}$ is the chirp mass (defined in Eq.~\ref{eq:chirp_mass}) and $e$ is the eccentricity and
\begin{equation}
    F(e) = \frac{1 + \frac{73}{24} e^2 + \frac{37}{96} e^4}{(1 - e^2)^{7/2}},
\end{equation}
is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}.

We can invert this and instead write that the chirp mass is
\begin{equation}
    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48} \frac{\dot{f}_{\rm orb}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
\end{equation}
and therefore that the chirp mass uncertainty is
\begin{equation}\label{eq:chirp_mass_uncertainty}
    \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} = \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} + \frac{3}{5} \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} + \frac{3}{5} \frac{\Delta F(e)}{F(e)}.
\end{equation}

We calculate the frequency uncertainties using \citet{Takahashi+2002}, such that
\begin{align}
    \frac{\Delta f_{\rm orb}}{f_{\rm orb}} &= 4 \sqrt{3} \cdot \frac{1}{\rho} \frac{1}{T_{\rm obs}} \frac{1}{f_{\rm orb}}, \\
    \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm orb}},
\end{align}
where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length. Then we calculate the eccentricity certainty as discussed in Sec.~\ref{sec:ecc_unc} and propagate it so that
\begin{equation}
    \frac{\Delta F(e)}{F(e)} = \Delta e \cdot \frac{(1256 + 1608 e^2 + 111 e^4) e}{96 + 196 e^2 - 255 e^4 - 37 e^6}.
\end{equation}

We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in the lower centre panel of Fig.~\ref{fig:fiducial_pdf_distributions}. We show the distribution as a CDF that is normalised to the expected number of detections to better indicate the absolute number of detections that will have well determined chirp masses. We find that approximately 10 BHBHs and BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region). We emphasise that this is a pessimistic estimate due to the pessimistic nature of how we determine the eccentricity uncertainty.

\subsubsection{Angular resolution}
